Typing a linear \picalc

### 2020-03-26 paper/paper.tex
Update examples
note on capability and multiplicity

@@

\todo{mention types are independent from capabilities}
\todo{add index to in-type}
\todo{update examples}

>>>>

\todo{Ornela: in linear pi if you write $\li$ the $\ell$ already means that the multiplicity is 1, meaning linear. 
We need to distinguish between \emph{capabilities} i, o or $\sharp$ and \emph{multiplicities} 0, 1 or $\omega$. So, the $\ell$ cannot be $\omega$, hence shared. You should use only i, o or $\sharp$ in Fig 7. and use $\ell$ as a syntactic sugar for i, o or $\sharp$ with multiplicity 1.}

@@

\todo{mention types are independent from capabilities}
